---
title: "create character csv"
author: "Mark Hancharik"
date: "10/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#[1]"strength", [2]"intelligence", [3]"wisdom" [4]"dexterity",[5]"constitution" ,[6]"charisma"

create_cleric = function(x){
  x[3] <- 8 + sample(1:10, 1) # min wis 9 
  #optional 
 # x[5] <- 7 + sample(1:11, 1) # min constitution 7 
 # x[4] <- 7 + sample(1:11, 1) # min dex 8 
 # x[1] <- 7 + sample(1:11, 1) # min str 8 
  x
}
create_druid = function(x){
  x[3] <- 11 + sample(1:7, 1) # min wis 12 
  x[6] <- 14 + sample(1:4, 1) # min wis 15 
  #optional 
#  x[5] <- 7 + sample(1:11, 1) # min constitution 7 
 # x[4] <- 7 + sample(1:11, 1) # min dex 8 
 # x[1] <- 7 + sample(1:11, 1) # min str 8 
  x
}
create_fighter = function(x){
  x[1] <- 8 + sample(1:10, 1) # min str 9
  x[5] <- 6 + sample(1:12, 1) # min con 7 
  #optional 
  
 # x[4] <- 7 + sample(1:11, 1) # min dex 8 
  
  x
}
create_paladin = function(x){
  x[1] <- 11 + sample(1:7, 1) # min str 12
  x[2] <- 8 + sample(1:10, 1) # min int 9 
  x[3] <- 12 + sample(1:6, 1) # min wis 13
  x[5] <- 8 + sample(1:10, 1) # min con 9
  x[6] <- 16 + sample(1:2, 1) # min chr 17 
  #optional 
  
 # x[4] <- 7 + sample(1:11, 1) # min dex 8 
  
  x
}

create_ranger = function(x){
  x[1] <- 12 + sample(1:6, 1) # min str 13
  x[2] <- 8 + sample(1:10, 1) # min int 13 
  x[3] <- 13 + sample(1:5, 1) # min wis 14
  x[5] <- 13 + sample(1:5, 1) # min con 14

  #optional 
  
 # x[4] <- 7 + sample(1:11, 1) # min dex 8 
  
  x
}
create_magic_user = function(x){
  x[2] <- 8 + sample(1:10, 1) # min int 9
  x[4] <- 5 + sample(1:13, 1) # min dex 6
 
  x
}
create_illusionist = function(x){
  x[2] <- 14 + sample(1:4, 1) # min int 15
  x[4] <- 15 + sample(1:3, 1) # min dex 16
 
  x
}
create_thief = function(x){
  
  x[4] <- 8 + sample(1:10, 1) # min dex 9
 # optional
  # x[2] <- 8 + sample(1:10, 1) # min int 9
  x
}
create_assassin = function(x){
  
  x[1] <- 11 + sample(1:7, 1) # min str 12
  x[2] <- 10 + sample(1:8, 1) # min int 11 
  x[4] <- 11 + sample(1:7, 1) # min dex 12
  x
}
create_monk = function(x){
  
  x[1] <- 14 + sample(1:4, 1) # min str 15
  x[3] <- 14 + sample(1:4, 1) # min wis 15 
  x[4] <- 14 + sample(1:4, 1) # min dex 15
  x[5] <- 10 + sample(1:4, 1) # min con 11
  x
}


create_class_stats = function(x,t){
  
#print(t)
 
  switch(t, 
        x <- create_cleric(x),
        x <- create_druid(x),
        x <- create_fighter(x),
        x <- create_paladin(x),
        x <- create_ranger(x),
        x <- create_magic_user(x),
        x <- create_illusionist(x),
        x <- create_thief(x),
        x <- create_assassin(x),
        x <- create_monk(x)
         )
      
    x[7] <- character_types[t]
  
  x
  
}


```





hlksdjhfa



```{r}

#u <- 6
character_types <- c("cleric","druid","fighter","paladin","ranger","magic_user","illusionist","thief","assassin","monk")
 
u <- length(character_types)*10^2  
characters <- matrix(NaN, u, 7)
#colnames(characters) <- c("strength","intelligence","wisdom", "dexterity", "constitution","charisma","class")
               

create_character = function(t){
  
  p<- c(2,2,2,2,2,2, "hippie")# 2 is test value, as 3 is minimum possible assigned score
  
  for(i in 1:6){
    test_values <- c(sample(1:6, 3, replace=TRUE))
    p[i] <- sum(test_values)
  }
  

 
  p <- create_class_stats(p, t)
  p
  
}

# generate a set of characters
for(i in 1:u){
  #print(i)
  digit <- (i %% length(character_types)) + 1
#print(digit)
characters[i,] <- create_character(digit)

}

#characters
#is.matrix(characters)
#is.data.frame(characters)
#write.csv(characters, file ="test.csv",quote = FALSE,row.names=FALSE, col.names = FALSE)
 write.table(characters, file="characters.csv", sep=',', quote = FALSE, row.names=FALSE, col.names=FALSE) 
  #write.csv(characters, file ="characters.csv",quote = FALSE,row.names=FALSE, col.names = FALSE)
 # write.table(characters, file ="characters.txt",quote = FALSE,row.names=FALSE, col.names = FALSE)

  

  
```

## old way

  if(i %% 6 == 1){
      characters[i,] <- make_fighter()
  character_types[i] = "fighter"
  }else if(i %% 6 == 2){
      characters[i,] <- make_fighter()
  character_types[i] = "wizard"
  }else if(i %% 6 == 3){
      characters[i,] <- make_fighter()
  character_types[i] = "theif"
  }else if(i %% 6 == 4){
      characters[i,] <- make_fighter()
  character_types[i] = "monk"
  }else if(i %% 6 == 5){
      characters[i,] <- make_fighter()
  character_types[i] = "illusionist"
  }else{
      characters[i,] <- make_fighter()
  character_types[i] = "priest"
  }
  
  
  
  
  
  
    head(iris)
  text_string <- '"1.8","1.1","1.9","0.3","mimosa"'
  cat(text_string)
  text_string <- gsub('"','', text_string)
  cat(text_string)
  text_string <- read.table("characters.csv", header=F)
   text_string
 text_string <- gsub('"','', text_string)
  text_string
   write.table(text_string, file ="fixed_characters.csv",row.names=FALSE)