---
title: "create character csv"
author: "Mark Hancharik"
date: "10/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

u <- 10002

characters <- matrix(NaN, u, 7)
#colnames(characters) <- c("strength", "dexterity", "speed" ,"intelligence","charisma","constitution","class")
character_types <- c("fighter","thief","ranger","mage","priest","monk")#vector(mode = "character", length = u)
                  

create_character = function(t){
  
  p<- c(2,2,2,2,2,2, "hippie")# 2 is test value, as 3 is minimum possible assigned score
  
  for(i in 1:6){
    test_values <- c(sample(1:6, 3, replace=TRUE))
    p[i] <- sum(test_values)
  }
 p[7] <- character_types[t]
  p[t] <- 14 + sample(1:4, 1) 
  
  p
  
}

# generate a set of characters
for(i in 1:u){
  #print(i)
  digit <- (i %% 6) + 1
#print(digit)
characters[i,] <- create_character(digit)

}

#characters


  write.csv(characters, file ="characters.csv",row.names=FALSE)
  write.table(characters, file ="characters.text",row.names=FALSE)


```

## old way

  if(i %% 6 == 1){
      characters[i,] <- make_fighter()
  character_types[i] = "fighter"
  }else if(i %% 6 == 2){
      characters[i,] <- make_fighter()
  character_types[i] = "wizard"
  }else if(i %% 6 == 3){
      characters[i,] <- make_fighter()
  character_types[i] = "theif"
  }else if(i %% 6 == 4){
      characters[i,] <- make_fighter()
  character_types[i] = "monk"
  }else if(i %% 6 == 5){
      characters[i,] <- make_fighter()
  character_types[i] = "illusionist"
  }else{
      characters[i,] <- make_fighter()
  character_types[i] = "priest"
  }