---
title: "party generator"
author: "Mark Hancharik"
date: "11/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}  
# I just needed this for illusionist and assasin, it was making me crazy
a_or_an = function(x){
  vowels <- c("a","e","i","o","u")
  pre_a <- "a"
  first_letter = substring(x, 1, 1)
  for(i in 1:length(vowels)){
    if(first_letter == vowels[i]){
      pre_a = "an"
    }
  }
  
  paste(pre_a,x)
  
}






# unsupervised machine learning 
recommender_system_engine = function(x){

# load a 'dummy' data frame that we know works   
dataset <- read.csv("one.csv", header=FALSE)
colnames(dataset) <-  c("strength","intelligence","wisdom", "dexterity", "constitution","charisma","class")
 
  
  for(i in 1:6){
  dataset[i] = x[i]
  }
  
character_model <- readRDS("./character_class_model_lda.rds")
character_prediction <- predict(character_model, dataset) 
#cat("the machine thinks you should be", a_or_an(as.character(character_prediction)),"\n")  
as.character(character_prediction)
}





```




```{r, echo=FALSE, warning=FALSE, message=FALSE}

library(caret)
library(mlbench)
library(randomForest)
library(doMC)
registerDoMC(cores=2) 

 #set.seed(1) 

attributes <- c("strength","intelligence","wisdom", "dexterity", "constitution","charisma")

values <- vector(mode = "integer", length = length(attributes))



party <- matrix(NA,6,1)
row.names(party) <- attributes

party_size = sample(3:8, 1, replace=TRUE)
cat("your party has",party_size,"members\n")





class_vector <- vector(mode = "character", length =party_size)
q_vector <- c("cleric","thief","fighter","illusionist","monk","druid","paladin","assassin")

for(z in 1:party_size){
  q <- "temp"#q_vector[1]
  #for(z in 1:100){ #       while(q!=q_vector[i]){
      for(i in 1:length(attributes)){
      this_atr <- c(sample(1:6, 3, replace=TRUE)) # 3d6
        values[i] <- sum(this_atr) # all 18's = "paladin", all 3's = "thief"
      }
  q <- recommender_system_engine(values)
  class_vector[z] <- q
  party <- cbind(party,values)
}


party <- party[,-1]
colnames(party) <- class_vector



party



##################################################
################# SHOW BAR PLOTS #################
##################################################

for(i in 1:party_size){
# barplot(party[,i],xlab = class_vector[i], ylab = "stats")
}

