---
title: "party generator"
author: "Mark Hancharik"
date: "11/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}  
# I just needed this for illusionist and assasin, it was making me crazy
a_or_an = function(x){
  vowels <- c("a","e","i","o","u")
  pre_a <- "a"
  first_letter = substring(x, 1, 1)
  for(i in 1:length(vowels)){
    if(first_letter == vowels[i]){
      pre_a = "an"
    }
  }
  
  paste(pre_a,x)
  
}




#simple
recommender_system_simple = function(x){
  if(x[1]> 13){
    cat("you would make a good fighter\n")
  }else{
    cat("not much of a fighter\n")
  }
}



# more complex
recommender_system_switch = function(x){
  switch(which.max(x),
   cat("a fighter you could be\n"), 
   cat("a magic_user you could be\n"), 
   cat("a cleric you could be\n"), 
   cat("a thief you could be\n"), 
   cat("a strong constitution you have\n"), 
   cat("a high charisma you have\n"))
  
}



# unsupervised machine learning 
recommender_system_engine = function(x){

# load a 'dummy' data frame that we know works   
dataset <- read.csv("one.csv", header=FALSE)
colnames(dataset) <-  c("strength","intelligence","wisdom", "dexterity", "constitution","charisma","class")
 
  
  for(i in 1:6){
  dataset[i] = x[i]
  }
  
character_model <- readRDS("./character_class_model_lda.rds")
character_prediction <- predict(character_model, dataset) 
#cat("the machine thinks you should be", a_or_an(as.character(character_prediction)),"\n")  
as.character(character_prediction)
}





```




```{r, echo=FALSE, warning=FALSE, message=FALSE}

library(caret)
library(mlbench)
library(randomForest)
library(doMC)
registerDoMC(cores=2) 

#set.seed(42) # set.seed(42) makes an assassin

attributes <- c("strength","intelligence","wisdom", "dexterity", "constitution","charisma")

values <- vector(mode = "integer", length = length(attributes))


for(i in 1:length(attributes)){
  this_atr <- c(sample(1:6, 3, replace=TRUE)) # 3d6
    values[i] <- sum(this_atr) # all 18's = "paladin", all 3's = "thief"
}

sheet <- cbind(attributes, values)

party <- matrix(NA,6,1)
row.names(party) <- attributes

#plot(sheet[,2], ylim=c(0,18), main='player attributes', col=values, legend = rownames(attributes), xlab = "attribute names")
#barplot(values, ylim=c(0,18),  main='player attributes', axisnames = TRUE,  names.arg=attributes, cex.names=0.8, col = )

#recommender_system_simple(values)
#recommender_system_switch(values)
created_vector <- vector(mode = "character", length =100)
q_vector <- c("cleric","thief","fighter","illusionist","monk","druid","paladin","assassin")
for(j in 1:length(q_vector)){
q <- "temp"#q_vector[1]
while(q!=q_vector[i]){
  for(i in 1:length(attributes)){
  this_atr <- c(sample(1:6, 3, replace=TRUE)) # 3d6
    values[i] <- sum(this_atr) # all 18's = "paladin", all 3's = "thief"
}
  q <- recommender_system_engine(values)
  #(mat.app <- cbind(party,values))
  #print(q)
}
  party <- cbind(party,values)
}
#party <- na.omit(party)
q_vector <- c("hippie",q_vector)
colnames(party) <- q_vector
#party
#q <- recommender_system_engine(values)
#q
#sheet

good_party <- party[,-1]

good_party

for(i in 1:6){
# barplot(good_party[,i],xlab = q_vector[i+1], ylab = "stats")
 # plot(good_party[,i],xlab = q_vector[i+1], ylab = "stats")
}

